Mathematical Formulation of Projection Problem

### 2025-03-12 docs/logbook.tex
Got the projection code finished

>>>>

	\begin{MeetingMinutes}{Sat 8/3/2025}{u7013004}
		Important to have no nothing days. Today, I will write more about SfM in my thesis. The goal of the long weekend will be to have results of the mesh changing.
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Wed 12/03/2025}{u7013004}
		Turns out the SciPy was hanging because it takes 4 minutes per iteration when using a subdivision level of 4. Takes 10 seconds if subdivision level of 3, and basically instant with subdivision level of 2. I think including the manually providing the gradients should speed up the computation.

		Today, I want to write the code for the node and make sure that it works for subdiv levels 2 and 3. After that, I want to write the Chamfer distance loss function and hook it up. Then I'd like to visualise the results. Should be good!
	\end{MeetingMinutes}
